MCTS Based on Simple Regret

### 2012-03-14 paper/srcr/paper.tex
answers to the questions
fixed illustration

\begin{dfn}
The \textbf{simple regret} of a sampling policy for the Multi-armed Bandit
Problem is the expected difference between the best expected reward
$\mu_*$ and the expected reward $\mu_j$ of the empirically best arm
$\overline X_j=\max_i\overline X_i$:
\begin{equation}
\IE r=\sum_{j=1}^K\Delta_j\Pr(\overline X_j=\max_i\overline X_i)
\label{eqn:simple-regret}
\end{equation}
where $\Delta_j=\mu_*-\mu_j$.
\end{dfn}

@@

\begin{algorithm}[h!]
\caption{Two-stage Monte-Carlo tree search sampling}
\label{alg:two-stage-mcts}
\begin{algorithmic}[1]
\Procedure{Rollout}{node, depth=1}
  \If {\Call{IsLeaf}{node, depth}}
    \State \textbf{return} 0
  \Else
    \State \textbf{if} depth=1 \textbf{then} action $\gets$ \Call{FirstAction}{node} \label{alg:srcr-first-action}   
    \State \textbf{else} action $\gets$ \Call{NextAction}{node} \label{alg:srcr-next-action}
    \State next-node $\gets$ \Call{NextState}{node, action}
    \State reward $\gets$ \Call{Reward}{node, action, next-node}
     \State \hspace{4em} + \Call{Rollout}{next-node, depth+1}
    \State \Call{UpdateStats}{node, action, reward}
  \EndIf
\EndProcedure
\end{algorithmic}
\end{algorithm}

>>>>

\begin{dfn}
The \textbf{simple regret} $\IE r$ of a sampling policy for the Multi-armed Bandit
Problem is the expected difference between the best expected reward
$\mu_*$ and the expected reward $\mu_j$ of the empirically best arm
$\overline X_j=\max_i\overline X_i$:
\begin{equation}
\IE r=\sum_{j=1}^K\Delta_j\Pr(\overline X_j=\max_i\overline X_i)
\label{eqn:simple-regret}
\end{equation}
where $\Delta_j=\mu_*-\mu_j$.
\end{dfn}

@@

\begin{algorithm}[h!]
\caption{Two-stage Monte-Carlo tree search sampling}
\label{alg:two-stage-mcts}
\begin{algorithmic}[1]
\Procedure{Rollout}{node, depth=1}
  \If {\Call{IsLeaf}{node, depth}}
    \State \textbf{return} 0
  \Else
    \State \textbf{if} depth=1 \textbf{then} action $\gets$ \Call{FirstAction}{node} \label{alg:srcr-first-action}   
    \State \textbf{else} action $\gets$ \Call{NextAction}{node} \label{alg:srcr-next-action}
    \State next-node $\gets$ \Call{NextState}{node, action}
    \State reward $\gets$ \Call{Reward}{node, action, next-node}
     \State \hspace{4em} + \Call{Rollout}{next-node, depth+1}
    \State \Call{UpdateStats}{node, action, reward}
    \State \textbf{return} reward
  \EndIf
\EndProcedure
\end{algorithmic}
\end{algorithm}
